Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-05 paper.qmd
Tried to update figure 16

tr_from_to_df_pbmc <- right_join(
  tr_from_to_df_pbmc, distance_df_small_edges_pbmc,
  by = c("from", "to"))

@@

@@

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = tsne_minst_scaled,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
  scale_color_manual(values=c("#999999",'#ff7f00')) +
  interior_annotation("a", c(0.08, 0.93), cex = 1.5) +
  theme(legend.position = "none")

>>>>

tr_from_to_df_pbmc <- right_join(
  tr_from_to_df_pbmc, distance_df_small_edges_pbmc,
  by = c("from", "to")) |>
  select(-ID)

@@

# tr_from_to_df_mnist <- tr_from_to_df_mnist |>
#   mutate(ID = row_number()) |>
#   filter(!(ID %in% c(1205, 1629, 1170)))

@@

trimesh_removed_mnist <- ggplot() + 
  geom_point(data = tsne_minst_scaled,
             aes(
               x = tSNE1,
               y = tSNE2,
               colour = cluster
             ),
             alpha=0.2)+
    geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000") +
  scale_color_manual(values=c("#999999",'#ff7f00')) +
  interior_annotation("a", c(0.08, 0.93), cex = 1.5) +
  theme(legend.position = "none")
